Mossy Pond mrmr model 1

### 2024-11-22 code/R/MossyPond_Classic_mrmr.Rmd
run updated model with new gen quants

```{r}
library(dplyr)
library(readr)
library(tibble)
library(rstan)
library(mrmr)
library(ggpubr)
```

@@

abundance_MP_classic <- plot_model(mrmr_mossy_mod1, "abundance")
recruitment_MP_classic <- plot_model(mrmr_mossy_mod1, "recruitment")

MP_classic_plots <- ggarrange(abundance_MP_classic, recruitment_MP_classic, ncol=1)
MP_classic_plots

>>>>

```{r}
library(dplyr)
library(readr)
library(tibble)
library(cmdstanr)
library(mrmr)
library(ggpubr)
```

@@

abundance_MP_classic <- plot_model(classic_mod_mp, "abundance")
recruitment_MP_classic <- plot_model(classic_mod_mp, "recruitment")

mp_classic_plots <- ggarrange(abundance_MP_classic, recruitment_MP_classic, ncol=1)

# add title
mp_classic_plots_annotated <- annotate_figure(mp_classic_plots, top = text_grob("Classic mrmr", size = 14, face = "bold"))

mp_classic_plots_annotated
